Superabsorption of light by nanoparticles

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs-rev-2015-10-08.tex
renamed files for upload
small changes

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Superabsorption of light by nanoparticles}} \\%Article title goes here instead of the text "This is the title"
 & \vspace{0.3cm} \\

 & \noindent\large{Konstantin Ladutenko,$^{\ast}$\textit{$^{a,b}$}
   Pavel Belov,\textit{$^{a}$} Ovidio
   Pe\~{n}a-Rodr\'{i}guez,\textit{$^{c}$} Ali Mirzaei,\textit{$^{d}$}
   Andrey Miroshnichenko,\textit{$^{d}$} and Ilya
  Shadrivov\textit{$^{d}$}} \\%Author names go here instead of "Full name", etc.

@@

\sffamily{\textbf{ Nanoparticles have a fundamental limit as to how
    much light they can absorb. This limit is based on the finite
    number of modes excited in the nanoparticle at a given wavelength
    and maximum absorption capacity per mode. The enhanced absorption
    can be achieved when each mode supported by the nanoparticle
    absorbs light up to the maximum capacity. Using stochastic
    optimization algorithm, we design multilayer nanoparticles, in
    which we can make several resonant modes overlap at the same
    frequency resulting in \textit{ superabsorption}.  We further
    introduce the \textit{ efficiency of the absorption} for a
    nanoparticle, which is the absorption normalized by the physical
    size of the particle, and show that efficient absorbers are not
    always operating in the superabsorbing regime.}}\\%The abstrast
goes here instead of the text "The abstract should be..."

%%%END OF ABSTRACT%%%%

@@

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{Fig1}%
    \caption{Shematic view of the simulated $Si/Ag/Si$ particle. 
      \label{fig:geom}
    }%
  }
\end{figure}

@@

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-Qabs-SiAgSi-overview}%
    \caption{Results of optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved for the particle of the
      double-layer Ag/Si design of the radius of 36~nm. Dashed lines
      show theoretical limits for the first channel and second channel
      absorption. The second and third peaks in the absorption
      efficiency curve exceed the theoretical limit for the second
      mode absorption at $R=63$~nm and $R=81$~nm. Local maxima of
      absorption efficiency are additionally marked with arrows. (b)
      Mie absorption coefficients for individual excited modes of the
      optimized structures. (c) Optimized layer thicknesses. For the
      total particle radius below 46~nm the optimizer converges to a
      bi-layer structure, when core size vanishes, and the optimum
      design is a $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency. We maximize absorption efficiency at a fixed wavelength of
the incident light (we have chosen $\lambda=500$~nm). We show the
results of our stochastic optimization algorithm in
Fig.~\ref{fig:overview}~(a).  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances,\cite{Tribelsky-2011} which are given as \[Q^{(n)}_{\rm
  abs\ max}=\frac{2n+1}{2q^2},\] where the size parameter $q=2\pi
R/\lambda$, and $n$ is the angular momentum of the mode. Following
Ref.\cite{Fan-2011}, where the authors introduce superscattering for
spherical particles, here we introduce superabsorption regime, when
{\em the ACS is larger than the theoretical limit for absorption by
  strongly excited mode with the highest angular momentum $n$}. In our
parameter space we have modes up to the quadrupole excited ($n=2$),
and in order to get superabsorption our efficiency should be higher
than that of a quadrupole. We clearly see this superabsorption regime
at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).

@@

@@

Remarkably, the absolute maximum {\em absorption efficiency} is not
reached within the superabsorption regime. Figure~\ref{fig:overview}
shows that the maximum efficiency is achieved for small particle size,
and the ACS is still well below the single channel limit. It appears
that the $Ag/Si$ core-shell nanoparticle with the total radii of
approximately 36~nm is the most efficient absorber among the
considered structures, whose ACS reaches values {\em over 5 times the
  physical cross-section area of the particle}.  From a practical
point of view, it is quite important that the maximum can be reached
in a bi-layer structure, instead of a triple-layer, since it should be
easier and cheaper to fabricate. At the same time the best absorption
efficiency for larger particles (with $R>60$~nm for provided
materials) can be achieved in superabsorption regime. This may be
important when fabrication of smaller multi-layer particles is not
available.

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer
      of design from panel~(c), and it explains an almost
      flat top of the electric dipole resonance.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to the incident wave.  White curves show the
      energy flow streamlines; plane wave comes from the left.
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
Using semi-transparent white curves we also plot streamlines of the
Poynting vector which characterize energy flow.  For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of superabsorption regime, we
observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a superabsorbing design is
obvious: spatial distribution of the electric field is not uniform
inside the particle and the share of the volume with high absorption
rate in the vortices does not compensate low absorption efficiency in
the regions with small electric field (absorbed power is expressed as
$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to the strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proven
to have a wide absorption band~\cite[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

@@

  Authors wish to thank David A. Powell for useful discussions.  AEM
  and IVS acknowledge the support from the Australian Research Council
  through Future Fellow and Discovery Project schemes. OPR is grateful
  to Consejo Nacional de Ciencia y Tecnolog\'{i}a (Mexico) for
  financing a short stay at Universidad Autónoma de Puebla, Mexico.
  KSL and PAB thank the Ministry of Education and Science of the
  Russian Federation and Government of the Russian Federation (Grant
  074-U01) for the financial support.

@@

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

\balance

@@

%%%REFERENCES%%%
\scriptsize{
%\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
\bibliography{2015-Ladutenko-Qabs}
\bibliographystyle{rsc} } %the RSC's .bst file

>>>>

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Superabsorption of light by nanoparticles}} \\
 & \vspace{0.3cm} \\

 & \noindent\large{Konstantin Ladutenko,$^{\ast}$\textit{$^{a,b}$}
   Pavel Belov,\textit{$^{a}$} Ovidio
   Pe\~{n}a-Rodr\'{i}guez,\textit{$^{c}$} Ali Mirzaei,\textit{$^{d}$}
   Andrey Miroshnichenko,\textit{$^{d}$} and Ilya
  Shadrivov\textit{$^{d}$}} \\

@@

\sffamily{\textbf{ Nanoparticles have a fundamental limit as to how
    much light they can absorb. This limit is based on the finite
    number of modes excited in the nanoparticle at a given wavelength
    and maximum absorption capacity per mode. The enhanced absorption
    can be achieved when each mode supported by the nanoparticle
    absorbs light up to the maximum capacity. Using stochastic
    optimization algorithm, we design multilayer nanoparticles, in
    which we can make several resonant modes overlap at the same
    frequency resulting in \textit{ superabsorption}.  We further
    introduce the \textit{ efficiency of the absorption} for a
    nanoparticle, which is the absorption normalized by the physical
    size of the particle, and show that efficient absorbers are not
    always operating in the superabsorbing regime.}}
%%%END OF ABSTRACT%%%%

@@

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{Fig1}%
    \caption{Shematic view of the simulated $Si/Ag/Si$ particle. 
      \label{fig:geom}
    }%
  }
\end{figure}

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-Qabs-SiAgSi-overview}%
    \caption{Results of optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved for the particle of the
      double-layer Ag/Si design of the radius of 36~nm. Dashed lines
      show theoretical limits for the first channel and second channel
      absorption. The second and third peaks in the absorption
      efficiency curve exceed the theoretical limit for the second
      mode absorption at $R=63$~nm and $R=81$~nm. Local maxima of
      absorption efficiency are additionally marked with arrows. (b)
      Mie absorption coefficients for individual excited modes of the
      optimized structures. (c) Optimized layer thicknesses. For the
      total particle radius below 46~nm the optimizer converges to a
      bi-layer structure, when core size vanishes, and the optimum
      design is a $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}

@@

In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency. We maximize absorption efficiency at a fixed wavelength of
the incident light (we have chosen $\lambda=500$~nm). We show the
results of our stochastic optimization algorithm in
Fig.~\ref{fig:overview}~(a).  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances,\cite{Tribelsky-2011} which are given as \[Q^{(n)}_{\rm
  abs\ max}=\frac{2n+1}{2q^2},\] where the size parameter $q=2\pi
R/\lambda$, and $n$ is the angular momentum of the mode. Following
Ref.\cite{Fan-2011}, where the authors introduce superscattering for
spherical particles, here we introduce superabsorption regime, when
{\em the ACS is larger than the theoretical limit for absorption by
  strongly excited mode with the highest angular momentum $n$}. In our
parameter space we have modes up to the quadrupole excited ($n=2$),
and in order to get superabsorption our efficiency should be higher
than that of a quadrupole. We clearly see this superabsorption regime
at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).

@@

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer
      of design from panel~(c), and it explains an almost
      flat top of the electric dipole resonance.
      \label{fig:spectra}
    }%
  }
\end{figure}

@@

Remarkably, the absolute maximum {\em absorption efficiency} is not
reached within the superabsorption regime. Figure~\ref{fig:overview}
shows that the maximum efficiency is achieved for small particle size,
and the ACS is still well below the single channel limit. It appears
that the $Ag/Si$ core-shell nanoparticle with the total radii of
approximately 36~nm is the most efficient absorber among the
considered structures, whose ACS reaches values {\em over 5 times the
  physical cross-section area of the particle}.  From a practical
point of view, it is quite important that the maximum can be reached
in a bi-layer structure, instead of a triple-layer, since it should be
easier and cheaper to fabricate. At the same time the best absorption
efficiency for larger particles (with $R>60$~nm for provided
materials) can be achieved in superabsorption regime. This may be
important when fabrication of smaller multi-layer particles is not
available.
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
Using semi-transparent white curves we also plot streamlines of the
Poynting vector which characterize energy flow.  For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of superabsorption regime, we
observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a superabsorbing design is
obvious: spatial distribution of the electric field is not uniform
inside the particle and the share of the volume with high absorption
rate in the vortices does not compensate low absorption efficiency in
the regions with small electric field (absorbed power is expressed as
$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to the incident wave.  White curves show the
      energy flow streamlines; plane wave comes from the left.
      \label{fig:field}
    }%
  }
\end{figure}

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to the strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proven
to have a wide absorption band~\cite{ACS-AMI-Liu-2015}. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

@@

  Authors wish to thank David A. Powell for useful discussions.  AEM
  and IVS acknowledge the support from the Australian Research Council
  through Future Fellow and Discovery Project schemes. OPR is grateful
  to Consejo Nacional de Ciencia y Tecnolog\'{i}a (Mexico) for
  financing a short stay at Universidad Autónoma de Puebla, Mexico.
  KSL and PAB thank the Ministry of Education and Science of the
  Russian Federation and Government of the Russian Federation (Grant
  074-U01) for the financial support.
%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
\balance

@@

@@

%%%REFERENCES%%%
\scriptsize{
%\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
\bibliography{2015-Ladutenko-Qabs-rev-2015-10-08}
\bibliographystyle{rsc} } %the RSC's .bst file
